\section{Problem Formulation}
Our goal is to output the best detections at some deadline $F$, and to continue having the best detections at every time step after that.
Specifically, we seek to maximize the AP of a detector for all classes in all images of a test dataset.
\note{but see todo note in~\autoref{sec:evaluation}.}

In the limit of infinite time, our program will look everywhere for everything, but given a short deadline, it should first look in the most promising places for the most likely objects.
To take advantage of semantic and spatial context, where it looks at time $t$ should depend on the results gathered by $t-1$.

In each of the $I$ images we consider, we look for $K$ classes of objects, and have detectors $d_k$, with each one having some number $P_k$ of part fittings, cascade stages, or other partial classifiers $c_{kp}$.

We represent an image as a collection of overlapping windows at different scales: a multi-scale pyramid of $N$ locations $\l_i = (x,y,s)$ (the discretization and feautirzation of the image pyramid is discussed in~\autoref{sec:discretization_and_featurization}).
We assume that each location $\ell$ can be the center of at most one bounding box, containing an object belonging to one of $K$ classes.
While this assumption may not hold in cases of occlusion, it does hold for the data we consider and at the levels of discretization we use. \note{is this true?}

\aside{
There are two ways we could think about our task.
The first can be called ``assigning content to locations.''
It fits the sliding-window paradigm.
The second can be called ``assigning locations to content.''
It is inspired by particle filtering and the like~\cite{Gualdi2010}.
We'll mostly talk in the paradigm of the former, but these are two sides of the same coin.
}

We first describe a partially observable Markov decision process representing our problem.
Although we do not commit to using the methodology of solving POMDPs, this section is important, as it describes the specific models we assume, which even a hard-coded solution will use.

We can consider three variants of object detection as a sequential decision problem:
\begin{enumerate}
  \item Looking for everything at a location: Selecting a location $i$, and running a black box program $P$ there that evaluates all detectors as it sees fit.
  \item Looking for something at a location: Selecting a location $i$ and a detector $d_k$. Picking the sequence of partial classifiers for $d$ is then a black box subproblem.
\item Looking for partial evidence of something at a location: Selecting a location $i$ and a partial classifier $c_{kp}$.
\end{enumerate}
We will be working mostly at the level of the third problem in the following sections, although our initial implementations may start out at lower levels.

\input{pomdp_approach.tex}