% !TEX root = paper/paper.tex
\section{Related Work}
% \paragraph{Feature combination and selection.}
% \emph{Boosting} is a method for combining weak learners into a more powerful classifier \cite{Hastie2009}.
% A popular use of boosting is in introducing non-linearities by training depth-limited decision trees as weak learners---the boosting trick.
% For SVM-based classifiers, \emph{Multiple Kernel Learning} (MKL) provides a way to train classifiers using an automatically weighted combination of kernels \cite{Lanckriet2004}.
% It has been shown that MKL is outperformed by boosting single-kernel classifiers \cite{Gehler2009}.
% Of course, if all classifiers are linear, then combining outputs of classifiers trained on different feature channel with another classifier is equivalent to training one classifier on all features at once.
% \todo{What about learning a \emph{non-linear} second classifier on top of the weak learner scores---any papers?}

% \todo{A couple of sentences on feature selection approaches, particularly using infogain as proxy for classification error.}

\paragraph{Static selection}% test-time efficient feature selection.}
% The simplest way to limit the number of features used at test time is to $L_1$-regularize.
% This method does not explicitly consider feature cost, nor is it able to evaluate features one by one, or to give an answer before all features are computed.

A well-known method to evaluate features sequentially is the cascaded boosted classifier of Viola \& Jones \cite{Viola2004} (updated by Bourdev \& Brandt \cite{Bourdev-CVPR-2005} with a soft threshold), which is able to quit evaluating an instance before all features are computed---but feature cost was not considered.
The cost-sensitive cascade of Chen et al.\ \cite{Chen-AISTATS-2012} optimizes stage order and thresholds to jointly minimize classification error and feature computation cost.
Xu et al.\ \cite{Xu-ICML-2012} and Grubb \& Bagnell \cite{Grubb-AISTATS-2012} separately develop a variant of gradient boosting for training cost-sensitive classifiers; the latter prove near-optimality of their greedy algorithm with submodularity results.
Their methods are tightly coupled to the stage-wise regression algorithm.

\vspace{-1em}
\paragraph{Dynamic selection}% test-time efficient feature selection.}
The above methods learn an efficient but \emph{fixed} order for evaluating features given a test instance.

Gao \& Koller \cite{Gao-NIPS-2011} propose a method for \emph{active classification}: myopically selecting the next feature based on expected information gain given the values of the already selected features.
The method is based on locally weighted regression, highly costly at test time.
Ji \& Carin \cite{Ji-PR-2007} also formulate cost-sensitive feature selection generatively, as an HMM conditioned on actions, but select actions myopically, again at signficant test time cost.

Karayev at al.\ \cite{Karayev-NIPS-2012} propose a reinforcement learning approach for selecting object detectors; they rely on expensive test-time inference in a graphical model to combine observations.
Dulac-Arnold et al.\ \cite{Dulac-Arnold-ML-2012} present another MDP-based solution to ``datum-wise classification'', with an action space comprised of all features and labels, recently extended to region-based processing \cite{Dulac-Arnold-ICLR-2014}.
He He et al.\ \cite{HeHe-ICMLW-2012} also formulate an MDP with features and a single classification step as actions, but solve it via imitation learning of a greedy policy.
Benbouzid et al.\ \cite{Benbouzid-ICML-2012} formulate an MDP that simply extends the traditional sequential boosted classifier with an additional \emph{skip} action, significantly limiting the space of learnable policies (\cite{Trapeznikov} provides another variation on this problem).
Although \cite{Karayev-NIPS-2012} targets \emph{Anytime} performance, their inference procedure is prohibitively expensive for test-time use in a general classification task.
In contrast, our fast linear method allows direct specification of the Anytime cost budget.

\emph{Label trees} also guide an instance through a tree of classifiers; their structure is determined by the confusion matrix or learned jointly with weights \cite{Deng-NIPS-2011}.
Xu et al.\ \cite{Xu-ICML-2013} learn a cost-sensitive binary tree of weak learners using an approach similar to the cyclic optimization of \cite{Chen-AISTATS-2012}.
Less directly related---but exciting for its novelty---is the work of \cite{weiss2013dynamic}, who apply simple introspection to structured models for a significant speedup of human pose estimation.
Another exciting direction is theoretical analysis of near-optimal policies with humans in the loop \cite{chen14active}.
